Predicting Audio Features with Last.fm Tags

### 2023-05-11 paper/main.tex
improved results table and more details about kaggle dataset

Considering that the data was gathered from a single user,
we explored the data to verify that the distribution of the Spotify audio features
was comparable to other Spotify datasets.
In particular, we verified that the distribution of the features,
described in Table \ref{table:audio-features-stats} and Figure \ref{fig:audio-features-distribution},
was comparable to the distribution of the \emph{Spotify Audio Features} Kaggle dataset
\footnote[6]{https://www.kaggle.com/datasets/tomigelo/spotify-audio-features}.

\begin{table}[h!]
      \begin{center}
      \begin{minipage}{\textwidth}
      \caption{Audio features description}\label{table:audio-features-stats}%
      \begin{tabular}{@{}lll@{}}
      \toprule
      Feature           & $\mu$ & $\sigma$ \\
      \midrule
      Danceability      & 0.599  & 0.193  \\
      Energy            & 0.631  & 0.233  \\
      Acousticness      & 0.221  & 0.302  \\
      Instrumentalness  & 0.514  & 0.382  \\
      Valence           & 0.435  & 0.279  \\
      \botrule
      \end{tabular}
      \end{minipage}
      \end{center}
\end{table}

\begin{figure}[h!]
      \centering
      \includegraphics[width=\textwidth]{images/features-distribution.png}
      \caption{Distribution of audio features. These densities are similar to the values shown by the \emph{Spotify Audio Features} Kaggle dataset.}
      \label{fig:audio-features-distribution}
\end{figure}

@@

@@

      Tree      & 1000 tags                           & 0.149            & 0.249           & 0.184     & 0.236      & 0.291          \\
      Bayes     & 10000 tags                          & 0.152            & 0.251           & 0.189     & 0.236      & 0.297          \\
      Tree      & 10000 tags                          & 0.148            & 0.250           & 0.181     & 0.236      & 0.290          \\

@@

      .....     & .............                       & .....            & .....           & .....     & .....      & .....          \\
      GPT       & Duplicated\footnotemark[2]          & 0.157            & ...             & ...       & ...        & ...            \\
      GPT       & Ordered\footnotemark[3]             & 0.149            & ...             & ...       & ...        & ...            \\
      GPT       & Tags,Counts\footnotemark[4]         & \textbf{0.145}   & ...             & ...       & ...        & ...            \\
      \botrule
      \end{tabular}
      \footnotetext[1]{Tags in tabular format. Given $(rock, 3)$, the cell in the $rock$ column contains \verb*|3|.}
      \footnotetext[2]{Duplicated tokens in tabular format. Tags $(rock, 3), (pop, 2)$, are converted to the \verb*|"rock, rock, rock, pop, pop"| string, 
      which a tokenizer converts to the list of input tokens (e.g. \verb*|[101,1005,16588,1005,2531, ...]|).
      These tokens are passed to the model in tabular format. Columns are $token_1$, $token_2$, $...$, $token_N$.}
      \footnotetext[3]{Ordered tokens in tabular format. Tags $(rock, 3), (pop, 2)$, are converted to the \verb*|"rock, pop"| string,
      which a tokenizer converts to the list of input tokens (e.g. \verb*|[101,1005,16588,1005,2531, ...]|).
      These tokens are passed to the model in tabular format. Columns are $token_1$, $token_2$, $...$, $token_N$.}
      \footnotetext[4]{Tokens in tabular format from tags and counts. Tags $(rock, 3), (pop, 2)$, are converted to the \verb*|"'rock' 3, 'pop' 2"| string,
      which a tokenizer converts to the list of input tokens (e.g. \verb*|[101,1005,16588,1005,2531, ...]|).
      These tokens are passed to the model in tabular format. Columns are $token_1$, $token_2$, $...$, $token_N$.}
      \footnotetext[2]{String. Given tags $(rock, 3), (pop, 2)$, input is formatted as \verb*|"rock, rock, rock, pop, pop"|.}
      \footnotetext[3]{String. Given tags $(rock, 3), (pop, 2)$, input is formatted as \verb*|"rock, pop"|.}
      \footnotetext[4]{String. Given tags $(rock, 3), (pop, 2)$, input is formatted as \verb*|"'rock' 3, 'pop' 2"|.}
      \end{minipage}
      \end{center}
\end{table}

>>>>

Considering that the data was gathered from a single user,
we explored the data to verify that the distribution of the Spotify audio features
was comparable to other Spotify datasets.
In particular, we verified that the distribution of the features,
described in Table \ref{table:audio-features-stats} and Figure \ref{fig:audio-features-distribution},
was comparable to the distribution of the \emph{Spotify Audio Features} Kaggle dataset.
This dataset contains more tha 116,000 unique tracks, and includes audio features for each track.
Our dataset present similar $\mu$ and $\sigma$ values as the Spotify Audio Features Kaggle dataset,
as illustrated in Table \ref{table:audio-features-stats-kaggle} and Figure \ref{fig:audio-features-distribution-kaggle}.
\footnote[6]{https://www.kaggle.com/datasets/tomigelo/spotify-audio-features}.

% Another dataset created from the Spotify API and published to Kaggle:
% https://www.kaggle.com/datasets/andrewmvd/spotify-playlists

\begin{table}[h!]
      \begin{center}
      \begin{minipage}{\textwidth}
      \caption{Audio features description}\label{table:audio-features-stats}%
      \begin{tabular}{@{}lll@{}}
      \toprule
      Feature           & $\mu$ & $\sigma$ \\
      \midrule
      Danceability      & 0.60  & 0.19  \\
      Energy            & 0.63  & 0.23  \\
      Acousticness      & 0.22  & 0.30  \\
      Instrumentalness  & 0.51  & 0.38  \\
      Valence           & 0.44  & 0.28  \\
      \botrule
      \end{tabular}
      \end{minipage}
      \end{center}
\end{table}
\begin{table}[h!]
      \begin{center}
      \begin{minipage}{\textwidth}
      \caption{Audio features description of \emph{Spotify Audio Features} Kaggle dataset}\label{table:audio-features-stats-kaggle}%
      \begin{tabular}{@{}lll@{}}
      \toprule
      Feature           & $\mu$ & $\sigma$ \\
      \midrule
      Danceability      & 0.58   & 0.19  \\
      Energy            & 0.57  & 0.26  \\
      Acousticness      & 0.34  & 0.25  \\
      Instrumentalness  & 0.22  & 0.36  \\
      Valence           & 0.44  & 0.26  \\
      \botrule
      \end{tabular}
      \end{minipage}
      \end{center}
\end{table}

\begin{figure}[h!]
      \centering
      \includegraphics[width=\textwidth]{images/features-distribution.png}
      \caption{Distribution of audio features in our single-user dataset.}
      \label{fig:audio-features-distribution}
\end{figure}

\begin{figure}[h!]
      \centering
      \includegraphics[width=\textwidth]{images/feature-distribution-kaggle.png}
      \caption{Distribution of audio features in the \emph{Spotify Audio Features} Kaggle dataset.}
      \label{fig:audio-features-distribution-kaggle}
\end{figure}

@@

      Bayes     & 10000 tags                          &\textbf{0.152}    &\textbf{0.251}   &\textbf{0.189}  &\textbf{0.236}   &\textbf{0.297}  \\

@@

      Tree      & 1000 tags                           & 0.149            &\textbf{0.249}   & 0.184          & 0.236           & 0.291          \\
      Tree      & 10000 tags                          &\textbf{0.148}    & 0.250           &\textbf{0.181}  &\textbf{0.235}   &\textbf{0.290}  \\

@@

      GPT       & Duplicated\footnotemark[5]          & 0.157            & ...             & ...            & ...             & ...            \\
      GPT       & Ordered\footnotemark[6]             & 0.149            & ...             & ...            & ...             & ...            \\
      GPT       & Tags,Counts\footnotemark[7]         & \textbf{0.145}   & ...             & ...            & ...             & ...            \\

      \botrule
      \end{tabular}
      \footnotetext[1]{Tags in tabular format. Given $(rock, 3)$, the cell in the $rock$ column contains \verb*|3|.}
      \footnotetext[2]{Duplicated tokens in tabular format. Tags $(rock, 3), (pop, 2)$, are converted to the \verb*|"rock, rock, rock, pop, pop"| string,
      which a tokenizer converts to the list of input tokens (e.g. \verb*|[101,1005,16588,1005,2531, ...]|).
      These tokens are passed to the model in tabular format. Columns are $token_1$, $token_2$, $...$, $token_N$.}
      \footnotetext[3]{Ordered tokens in tabular format. Tags $(rock, 3), (pop, 2)$, are converted to the \verb*|"rock, pop"| string,
      which a tokenizer converts to the list of input tokens (e.g. \verb*|[101,1005,16588,1005,2531, ...]|).
      These tokens are passed to the model in tabular format. Columns are $token_1$, $token_2$, $...$, $token_N$.}
      \footnotetext[4]{Tokens in tabular format from tags and counts. Tags $(rock, 3), (pop, 2)$, are converted to the \verb*|"'rock' 3, 'pop' 2"| string,
      which a tokenizer converts to the list of input tokens (e.g. \verb*|[101,1005,16588,1005,2531, ...]|).
      These tokens are passed to the model in tabular format. Columns are $token_1$, $token_2$, $...$, $token_N$.}
      \footnotetext[5]{String. Given tags $(rock, 3), (pop, 2)$, input is formatted as \verb*|"rock, rock, rock, pop, pop"|.}
      \footnotetext[6]{String. Given tags $(rock, 3), (pop, 2)$, input is formatted as \verb*|"rock, pop"|.}
      \footnotetext[7]{String. Given tags $(rock, 3), (pop, 2)$, input is formatted as \verb*|"'rock' 3, 'pop' 2"|.}
      \end{minipage}
      \end{center}
\end{table}
